### 2021-04-21 architecture.tex
Update on Overleaf.

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following\iftoggle{LONG}{
sections (see also \cref{fig:architecture}):
\begin{itemize}
\item \Cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
\item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
\item \Cref{sec:output}: The output layer extracts symbol costs from the symbol embeddings.
\item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
\end{itemize}
}{
sections (see also \cref{fig:architecture}).
}

@@

As the first step of the recommender processing pipeline,
the input problem is converted from a \gls{cnf} representation
to a \emph{heterogeneous (directed) graph} \cite{Zhou2018}.
% Zhou uses the term "heterogeneous graph".
%\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
%We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
Each of the nodes of the graph is labeled with a node type,
and each edge is labeled with an edge type,
defining the heterogeneous nature of the graph.
Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
such as a clause, an atom or a predicate symbol.
Each such category of elements corresponds to one node type.
The edges represent the (oriented) relations between the elements,
for example the incidence relation between a clause and one of its (literals') atoms,
or the relation between an atom and its predicate symbol.
$\mathcal{R}$ denotes the set of all relations in the graph.
\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.

@@

The graph representation exhibits namely the following properties:
\begin{itemize}
\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
(up to logical equivalence).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item For each relation $r \in \mathcal{R}$, its inverse $\inv{r}$ is also present in the graph,
typically\todo{MS: jaka je vyjimka?} represented by a different edge type.
\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
%\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Sub-expression sharing \cite{Chvalovsky2019,Olsak2019,Rawson2020}:
\todo[inline]{MS: (Almost)}
\todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
Identical atoms and terms share a node representation.
\todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''!}
%Note that since each variable is bound by a clause,
%ground terms are shared across clauses,
%but non-ground terms are only shared within the context of a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo{FB: Mention other encodings that have been proposed by Mirek and Michael and compare ours to theirs.}

@@

The symbol embeddings are output by a \emph{\gls{rgcn}} \cite{Schlichtkrull2017},
which is a stack of \emph{graph convolutional layers}.
Each layer consists of a collection of differentiable modules---one module per edge type.
\todo[author=R1]{Are there just so many nodes in the layer as the types of graph edges in Figure 2, or is each edge in the whole graph (a large set) represented by a collection of modules?}
\todo[author=FB]{I propose we ignore this comment because I don't understand its point and I can't think of a straightforward way to improve the clarity of the relevant part of the paper.}
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then iteratively updates the embeddings by passing them through the convolutional layers.

@@

Once all the messages are computed,
they are aggregated at the destination nodes to form the new node embeddings.
Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
then passes the sum through an activation function $\sigma$ such as the \gls{relu},
and finally aggregates the messages across the edge types by summation,
yielding the new embedding $h_d^{(l+1)}$.

The following formula captures the complete update of embedding of node $d$ by layer $l$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses*{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
$$

@@

Let $\theta$ denote the vector of all the parameters of the whole \acrlong{nn} consisting of the \gls{gcn} and the output unit.
Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
we denote the cost of symbol $s_i$ predicted by the \acrlong{nn} as $c(i, P; \theta)$.
In the rest of this text,
we refer to the predicted cost of $s_i$ simply as $c(i)$
because the problem $P$ and the parameters $\theta$ are fixed in each respective context.

@@

$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost on a given problem
independent of the problem's signature size $n$,
provided the expected symbol cost $\mathbb{E}_i [c(i)]$ does not depend on $n$:
\begin{multline*}
\mathbb{E}_\pi [C(\pi)]
= \mathbb{E}_\pi \SquareBracket*{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
= Z_n \Parentheses*{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
= \mathbb{E}_i [c(i)]
\end{multline*}
\todo[author=FB]{Discuss variance of the precedence cost in addition to the expected value.}

@@

It is easy to see that all the precedences that sort the symbol costs in a non-increasing order
have the same precedence cost.
Since $\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}

@@

Approaching this task directly, as a regression problem,
runs into the difficulty of establishing sensible target cost values for the precedences in the training dataset,
especially when a wide variety of input problems is covered.
Approaching the task as binary classification of precedences
seems possible, but it is not clear which precedences should be a priori
labeled as positive and which as negative, to give a guarantee
that a precedence minimizing the precedence cost (i.e. the one obtained by sorting)
would be among the best in any good sense.
\todo{FB: I think we could ensure that the precedence that minimizes $C$ is relatively good, for example the best of the observed. I hope that ranking generalizes better to unseen precedences, but I am not sure whether it does and I haven't done an experiment to confirm that.}
% such as learning to detect the precedences that yield a successful proof search within the allocated time.

We cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
% Mohri2018: p. 239, chapter 10 Ranking
by training a classifier to decide which of a \emph{pair} of precedences is better, based on their costs.
We train the classifier in a way that ensures that better precedences are assigned lower costs.
The motivation for learning to order pairs of precedences
is that it allows learning on easy problems,
and that it may allow the system to generalize to precedences that are better than any of those seen during training.
\todo{FB: We should test this hypothesis by training on one problem in isolation.}
\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
modelu narizujeme, na ktere hodnoty ma cilit.
My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
a zaroven rafinovane menime ulohu z regresivni na classifikacni.\\
FB: Regrese $C$ neni jedina alternativa. Mohli bychom klasifikovat jednotlive precedence (viz text). Mohli bychom relaxovat pozadavek, ze setridena permutace je nejlepsi; stacila by "dost dobra". Zkusil jsem nejak vyargumentovat, proc je klasifikace dvojic lepsi nez klasifikace jednotlivych precedenci.}

@@

\Cref{fig:architecture} shows how the loss function is plugged into the recommender for the training.

>>>>

The recommender consists of modules that perform specific sub-tasks,
each of which is described in detail in one of the following\iftoggle{LONG}{
sections (see also \cref{fig:architecture}):
\begin{itemize}
\item \Cref{sec:graphifier}: The graph constructor transforms the input \gls{cnf} problem into a problem graph.
\item \Cref{sec:gcn}: The \gls{gcn} computes symbol embeddings from the problem graph.
\item \Cref{sec:output}: The output layer extracts symbol costs from the symbol embeddings.
\item \Cref{sec:sorting}: The final symbol precedence is obtained by sorting the symbols by their costs.
\end{itemize}
}{
sections (see also \cref{fig:architecture}).
}

@@

As the first step of the recommender processing pipeline,
the input problem is converted from a \gls{cnf} representation
to a \emph{heterogeneous (directed) graph} \cite{Zhou2018}.
% Zhou uses the term "heterogeneous graph".
%\footnote{Data mining literature often uses the term \gls{hin} \cite{Shi2015} for heterogeneous graphs.
%We prefer to conform to the terminology common in literature studying \glspl{gnn}.}
Each of the nodes of the graph is labeled with a node type,
and each edge is labeled with an edge type,
defining the heterogeneous nature of the graph.
Each node corresponds to one of the elements that constitute the \gls{cnf} formula,
such as a clause, an atom, or a predicate symbol.
Each such category of elements corresponds to one node type.
The edges represent the (oriented) relations between the elements,
for example the incidence relation between a clause and one of its (literals') atoms,
or the relation between an atom and its predicate symbol.
$\mathcal{R}$ denotes the set of all relations in the graph.
\Cref{fig:CnfSchema} shows the types of nodes and edges used in our graph representation.
\Cref{fig:GcnExample} shows an example of a graph representation of a simple problem.

@@

The graph representation exhibits, namely, the following properties:
\begin{itemize}
\item Lossless: The original problem can be faithfully reconstructed from the corresponding graph representation
(up to logical equivalence).
\item Signature agnostic: Renaming the symbols and variables in the input problem yields an isomorphic graph.
\item For each relation $r \in \mathcal{R}$, its inverse $\inv{r}$ is also present in the graph,
typically\todo{MS: jaka je vyjimka?} represented by a different edge type.
\todo{MS: tohle jsem nepochopil. Nemuzeme rict, ze (az na nejakou vyjimkou) jsou edges v obou smerech?\\
FB: Chci vyjasnit, ze inverzni edge ma jiny edge type.}
%\item A singleton node of type \ntype{problem} is connected to all the clauses of the problem.
\item The polarity of the literals is expressed by the type of the edge (\epos{} or \eneg{})
connecting the respective atom to the clause it occurs in.
\item For every non-equality atom and term, the order of its arguments is captured by a sequence of \ntype{argument} nodes chained by edges \cite{Rawson2020}.
\item The two operands of equality are not ordered.
This reflects the symmetry of equality.
\item Sub-expression sharing \cite{Chvalovsky2019,Olsak2019,Rawson2020}:
\todo[inline]{MS: (Almost)}
\todo[inline]{MS: Predpokladam ze dva ruzne ground literaly p(c) tam budou taky jen jendnou?\\
FB: Literaly nemaji nody. Atomy maji nody a polarita literalu je zakodovana v typu hrany, ktery jej spojuje s klauzuli.
MS: O to my, neslo. Slo o to, jestli se sdily ground termy mezi klauzulemi, ted uz dobry! :)}
Identical atoms and terms share a node representation.
\todo{FB: Cite some text about sub-expression sharing. Perhaps Rawson2020?}
\todo{MS: Ale mezitim se to tu zmenilo a ja prestavam chapat, co je ``Redundant''!}
%Note that since each variable is bound by a clause,
%ground terms are shared across clauses,
%but non-ground terms are only shared within the context of a clause.
\todo{FB: Remove as of little interest?}
\end{itemize}
\todo{FB: Reference appendix if we describe the representation in more detail there.}
\todo{FB: Mention other encodings that have been proposed by Mirek and Michael and compare ours to theirs.}

@@

The symbol embeddings are output by a \emph{\gls{rgcn}} \cite{Schlichtkrull2017},
which is a stack of \emph{graph convolutional layers}.
Each layer consists of a collection of differentiable modules---one module per edge type.
\todo[author=R1]{Are there just so many nodes in the layer as the types of graph edges in Figure 2, or is each edge in the whole graph (a large set) represented by a collection of modules?}
\todo[author=FB]{I propose we ignore this comment because I do not understand its point and I cannot think of a straightforward way to improve the clarity of the relevant part of the paper.}
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then iteratively updates the embeddings by passing them through the convolutional layers.

@@

Once all messages are computed,
they are aggregated at the destination nodes to form new node embeddings.
Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
then passes the sum through an activation function $\sigma$ such as the \gls{relu},
and finally aggregates the messages across the edge types by summation,
yielding the new embedding $h_d^{(l+1)}$.

The following formula captures the complete update of the embedding of node $d$ by layer $l$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses*{\sum_{s \in \mathcal{N}_d^r} \frac{1}{c_{s,d}} (W_r^{(l)} h_s^{(l)} + b_r^{(l)})}
$$

@@

Let $\theta$ denote the vector of all parameters of the whole \acrlong{nn} consisting of the \gls{gcn} and the output unit.
Given an input problem $P$ with signature $\Sigma = (s_1, \ldots, s_n)$,
we denote the cost of symbol $s_i$ predicted by the \acrlong{nn} as $c(i, P; \theta)$.
In the rest of this text,
we refer to the predicted cost of $s_i$ simply as $c(i)$
because the problem $P$ and the parameters $\theta$ are fixed in each respective context.

@@

$Z_n = \frac{2}{n(n+1)}$ is a normalization factor
that ensures the commensurability of precedence costs across signature sizes.
More precisely, normalizing by $Z_n$ makes the expected value of the precedence cost on a given problem
independent of the problem's signature size $n$,
provided the expected symbol cost $\mathbb{E}_i [c(i)]$ does not depend on $n$:
\begin{multline*}
\mathbb{E}_\pi [C(\pi)]
= \mathbb{E}_\pi \SquareBracket*{Z_n \sum_{i=1}^n i \cdot c(\pi(i))}
= Z_n \sum_{i=1}^n i \cdot \mathbb{E}_\pi [c(\pi(i))] \\
= Z_n \Parentheses*{\sum_{i=1}^n i} \mathbb{E}_i [c(i)]
= \frac{2}{n(n+1)} \frac{n(n+1)}{2} \mathbb{E}_i [c(i)]
= \mathbb{E}_i [c(i)]
\end{multline*}
\todo[author=FB]{Discuss the variance of the precedence cost in addition to the expected value.}

@@

It is easy to see that all precedences that sort the symbol costs in a non-increasing order
have the same precedence cost.
Since $\emptyset \neq \argmin_\rho C(\rho) \subseteq \argsort^- (c(1), \ldots, c(n))$,
each of the precedences in $\argsort^- (c(1), \ldots, c(n))$ has the cost $\min_\rho C(\rho)$.
It follows that $\argsort^- (c(1), \ldots, c(n)) \subseteq \argmin_\rho C(\rho)$.
\qed
\end{proof}

@@

Approaching this task directly, as a regression problem,
runs into the difficulty of establishing sensible target cost values for the precedences in the training dataset,
especially when a wide variety of input problems is covered.
Approaching the task as a binary classification of precedences
seems possible, but it is not clear which precedences should be a priori
labeled as positive and which as negative, to give a guarantee
that a precedence minimizing the precedence cost (i.e. the one obtained by sorting)
would be among the best in any good sense.
\todo{FB: I think we could ensure that the precedence that minimizes $C$ is relatively good, for example the best of the observed. I hope that ranking generalizes better to unseen precedences, but I am not sure whether it does and I haven't done an experiment to confirm that.}
% such as learning to detect the precedences that yield a successful proof search within the allocated time.

We cast the task as an instance of score-based ranking problem \cite{Mohri2018,Burges2005}
% Mohri2018: p. 239, chapter 10 Ranking
by training a classifier to decide which of a \emph{pair} of precedences is better based on their costs.
We train the classifier in a way that ensures that better precedences are assigned lower costs.
The motivation for learning to order pairs of precedences
is that it allows learning on easy problems,
and that it may allow the system to generalize to precedences that are better than any of those seen during training.
\todo{FB: We should test this hypothesis by training on one problem in isolation.}
\todo[inline]{MS: ta druha myslenka, o ktere jsem mluvil pred obedem, se deje nekde v tomhle odstavci.
Jasne je, ze chceme vypichnout uceni ze dvojic precedenci jako jeden z klicovych napadu. Trochu min jasne je, proc by teda dvojice mely byt dobre.
Ja mel pocit, ze kdyz jsme se vloni snazili na tenhle problem napasovat regresi, 
pusobilo ``neprirozene'' vnucovat modelu konkretni cisla z vampiru. Jasne, nejak to resila normalizace
(a muselo se davat pozor aby cisla davala smysl nejen napric problemy (jeden resi vsechno rychle, jiny obcas neresi -- penalizace)
ale i kvuli ruznym velikostem signatury. Coz teda tady mame porad.) ale porad tam bylo to, ze nejak z vnejsku
modelu narizujeme, na ktere hodnoty ma cilit.
My tady ale vime, ze nam na konkretnich hodnotach sybol costu nezalezi, 
a ze ani nemusi byt rozumne porovnavatelne mezi problemy,
jediny, co je dulezity, je, aby setridena permutace byla ta (to the best of model's knowledge) nejlepsi.
Takze ja bych shrnul, ze s dvojicema obchazime nutnost stanovovat konkretni target values pro regresi (``problem volby spolecnych jednotek velicin''?)
a zaroven rafinovane menime ulohu z regresivni na classifikacni.\\
FB: Regrese $C$ neni jedina alternativa. Mohli bychom klasifikovat jednotlive precedence (viz text). Mohli bychom relaxovat pozadavek, ze setridena permutace je nejlepsi; stacila by "dost dobra". Zkusil jsem nejak vyargumentovat, proc je klasifikace dvojic lepsi nez klasifikace jednotlivych precedenci.}

@@

\Cref{fig:architecture} shows how the loss function is plugged into the recommender for training.

### 2021-04-21 conclusion.tex
Update on Overleaf.

We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
Comparison against a conventional symbol precedence heuristic shows that using a \gls{gcn}
to consider the whole structure of the input problem is beneficial.
\todo{FB: Should we boast that the reduction of ranking to training 
of differentiable element scores is innovative? MS: Yes! Ideally (also) earlier.}

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help designing new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of the ATP on the random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these patterns to a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}

In addition to the symbol precedence,
\gls{kbo} is determined by symbol \emph{weights}.
In this work, we kept the symbol weights fixed to the value 1.
Learning to recommend symbol weights in addition to the precedences
represents an interesting avenue for future research.

The same applies to the idea of learning to recommend 
both the predicate and the function precedences using a single \gls{gcn}.
The joint learning, although more complex to design, could 
additionally discover interdependencies
between the effects of the function precedence and predicate precedence on the proof search,
while the current setup implicitly assumes that the effects are independent.
Finally, a higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
in one training batch.

>>>>

We have described a system that extracts useful symbol precedences from the graph representations of \gls{cnf} problems.
Comparison with a conventional symbol precedence heuristic shows that using a \gls{gcn}
to consider the whole structure of the input problem is beneficial.
\todo{FB: Should we boast that the reduction of ranking to training 
of differentiable element scores is innovative? MS: Yes! Ideally (also) earlier.}

A manual analysis of the trained recommender could produce new insights into how the choice of the symbol precedence influences the proof search,
which could in turn help design new efficient precedence generating schemes.
Indeed, a trained cost model summarizes the observed behaviours of an ATP with random precedences
and is able to discover patterns in them (as we know implicitly from its accuracy) 
despite their seemingly chaotic behaviour as perceived by a human observer.
The challenge is to extract these patterns in a human-understandable form.
\todo[inline,author=R2]{[...] the analysis of the key patterns used by the trained recommender (only hinted at as a future work in the conclusion) would have been much more interesting in my opinion.}

In addition to the symbol precedence,
\gls{kbo} is determined by symbol \emph{weights}.
In this work, we keep the symbol weights fixed to the value 1.
Learning to recommend symbol weights in addition to the precedences
represents an interesting avenue for future research.

The same applies to the idea of learning to recommend 
both the predicate and function precedences using a single \gls{gcn}.
The joint learning, although more complex to design, could 
additionally discover interdependencies
between the effects of function precedence and predicate precedence on the proof search,
while the current setup implicitly assumes that the effects are independent.
Finally, a higher training data efficiency could be achieved by considering all pairs of measured executions on a problem
in one training batch.

### 2021-04-21 evaluation.tex
Update on Overleaf.

All the experiments were run on a computer with
the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}) and
\SI{383}{GiB} RAM.
%the OS Ubuntu 20.04 and
%the Linux kernel 5.4.0-40-generic.
\todo{FB: Add version of Python and notable packages, namely DGL and TensorFlow. 
MS: Z tohohle bych vetsinu nebo vsechno prenesl do README na adrese vyse.
Stejne ten paper neobsahuje dost informaci na to, aby si to mohl po nas nekdo naprogramovat a spustit.
Tak uz muze byt uplne jedno, jakou mame verzi Linuxu...}

@@

We used the problem library \acrshort{tptp}~v7.4.0 \cite{Sutcliffe2017}
as the source of problems for training and evaluation of the recommender.
We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$ ($\card{\ProblemsTptp} = 17053$).

@@

The examples were generated by iterative sampling of $\ProblemsTptp$.
In each iteration, a problem $P \in \ProblemsTptp$ was chosen and \Vampire{} was executed twice on $P$
with two (uniformly) random predicate precedences and a common random function precedence.
The ``background'' random function precedence served as additional noise (in addition to the variability 
contained in \acrshort{tptp}) and made sure that the predicate precedence recommender
would not be able to rely on any specificities that would come from fixing function precedences in the training data.

The two executions were compared in terms of performance:
the predicate precedence $\PrecBetter$ was recognized as better than the predicate precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$,
if the proof search finished successfully with $\PrecBetter$
and if the number of iterations of the saturation loop with $\PrecBetter$ was smaller than with $\PrecWorse$.
\todo{FB: Use notation for saturation loop iterations if the notation was established earlier. 
If failure is denoted by $\infty$, we can simply use $<$.}
If one of the two precedences was recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ would be produced,
where $\PrecBetter$ was the better precedence,
and $\PrecWorse$ was the other precedence.
Otherwise, for example, if the proof search timed out on both precedences, we would go back to sampling another problem.
\todo{FB: Discuss: How come we mix examples in which both precedences terminate with examples in which only one precedence terminates?}

@@

The sampling continued until \num{1000000} examples were generated when training a predicate precedence recommender,
or \num{800000} examples in case of a function precedence recommender.
% sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
For example, while generating \num{1000000} examples for the predicate precedence dataset,
\num{5349} out of the \num{17053} problems yielded at least one example,
while the least explored problem was tried 19 times, and the most exploited problem 504 times.

@@

A symbol cost model was trained by gradient descent
on the precedence ranking task (see \cref{sec:ranking})
using the examples generated from $\ProblemsTrain$.
To avoid redundant computations, all examples generated from a problem were processed in the same training batch.
Thus, each training batch contained up to \num{128} problems and all the examples generated from these problems.
The symbol cost model was trained using the Adam optimizer \cite{Kingma2014}.
The learning rate started at \num{1.28e-3}
and was halved each time the loss on $\ProblemsTrain$ stagnated for 10 consecutive epochs.
% tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
\todo[author=R2]{Same comment as just above: "... Adam optimizer [15]. Learning rate..." -> "... Adam optimizer [15]: Learning rate..."}

%\subsubsection{Sample weighting}
The examples were weighted.
Each of the examples of problem $P$ contributed to the training with the weight $\frac{1}{s_P}$,
where $s_P$ was the number of examples of problem $P$ in the training set.
This ensured that each problem contributed to the training to the same degree irrespective of the relative numbers of examples.

@@

The results show that the \gls{gcn}-based model outperformed the \texttt{frequency} heuristic by a significant margin.
\todo{FB: Add links to Neptune runs?}
Since the predicate precedence recommender was trained against randomly distributed function precedences,
it is expected to perform well irrespective of the function precedence heuristic it is combined with, and conversely.
Combining the trained recommenders for predicate and function precedences manifested better performance
than any of the two in combination with the standard \texttt{frequency} heuristic,
outperforming the \texttt{frequency} heuristic by approximately \SI{4.8}{\percent}.

>>>>

All experiments were run on a computer with
the CPU Intel Xeon Gold 6140 (72 cores @ \SI{2.30}{GHz}) and
\SI{383}{GiB} RAM.
%the OS Ubuntu 20.04 and
%the Linux kernel 5.4.0-40-generic.
\todo{FB: Add the version of Python and notable packages, namely, DGL and TensorFlow.
MS: Z tohohle bych vetsinu nebo vsechno prenesl do README na adrese vyse.
Stejne ten paper neobsahuje dost informaci na to, aby si to mohl po nas nekdo naprogramovat a spustit.
Tak uz muze byt uplne jedno, jakou mame verzi Linuxu...}

@@

We used the problem library \acrshort{tptp}~v7.4.0 \cite{Sutcliffe2017}
as the source of problems for training and evaluation of the recommender.
We denote the set of all problems available for training and evaluation as $\ProblemsTptp$ ($\card{\ProblemsTptp} = 17053$).

@@

The examples were generated by iterative sampling of $\ProblemsTptp$.
In each iteration, a problem $P \in \ProblemsTptp$ was chosen and \Vampire{} was executed twice on $P$
with two (uniformly) random predicate precedences and a common random function precedence.
The ``background'' random function precedence served as additional noise (in addition to the variability 
contained in \acrshort{tptp}) and made sure that the predicate precedence recommender
would not be able to rely on any specificity that would come from fixing function precedences in the training data.

The two executions were compared in terms of performance:
the predicate precedence $\PrecBetter$ was recognized as better than the predicate precedence $\PrecWorse$,
denoted as $\Better{\PrecBetter}{\PrecWorse}{P}$,
if the proof search finished successfully with $\PrecBetter$
and if the number of iterations of the saturation loop with $\PrecBetter$ was smaller than with $\PrecWorse$.
\todo{FB: Use the notation for saturation loop iterations if the notation was established earlier. 
If failure is denoted by $\infty$, we can simply use $<$.}
If one of the two precedences was recognized as better,
the example $(P, \PrecBetter, \PrecWorse)$ would be produced,
where $\PrecBetter$ was the better precedence,
and $\PrecWorse$ was the other precedence.
Otherwise, for example, if the proof search timed out on both precedences, we would go back to sampling another problem.
\todo{FB: Discuss: How come we mix examples in which both precedences terminate with examples in which only one precedence terminates?}

@@

The sampling continued until \num{1000000} examples were generated when training a predicate precedence recommender,
or \num{800000} examples in the case of a function precedence recommender.
% sftp://cluster.ciirc.cvut.cz/home/bartefil/git/vampire-ml/out/20210108-generate-predicate/questions_generated
For example, while generating \num{1000000} examples for the predicate precedence dataset,
\num{5349} out of the \num{17053} problems yielded at least one example,
while the least explored problem was tried 19 times, and the most exploited problem 504 times.

@@

A symbol cost model was trained by gradient descent
on the precedence ranking task (see \cref{sec:ranking})
using the examples generated from $\ProblemsTrain$.
To avoid redundant computations, all examples generated from any given problem were processed in the same training batch.
Thus, each training batch contained up to \num{128} problems and all examples generated from these problems.
The symbol cost model was trained using the Adam optimizer \cite{Kingma2014}.
The learning rate started at \num{1.28e-3}
and was halved each time the loss on $\ProblemsTrain$ stagnated for 10 consecutive epochs.
% tf.keras.callbacks.ReduceLROnPlateau(monitor='loss', factor=0.5, patience=10)
\todo[author=R2]{Same comment as just above: "... Adam optimizer [15]. Learning rate..." -> "... Adam optimizer [15]: Learning rate..."}

%\subsubsection{Sample weighting}
The examples were weighted.
Each of the examples of problem $P$ contributed to the training with the weight $\frac{1}{s_P}$,
where $s_P$ was the number of examples of problem $P$ in the training set.
This ensured that each problem contributed to the training to the same degree irrespective of the relative number of examples.

@@

The results show that the \gls{gcn}-based model outperformed the \texttt{frequency} heuristic by a significant margin.
\todo{FB: Add links to Neptune runs?}
Since the predicate precedence recommender was trained with randomly distributed function precedences,
it was expected to perform well irrespective of the function precedence heuristic it is combined with, and conversely.
Combining the trained recommenders for predicate and function precedences manifested better performance
than any of the two in combination with the standard \texttt{frequency} heuristic,
outperforming the \texttt{frequency} heuristic by approximately \SI{4.8}{\percent}.
